Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-10-23 saner/paper.tex
Related work

\subsubsection{Preconditions}
Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \ref{tsantalis2015assessing}:
\begin{enumerate}
  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependences.
  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependences.
  \item The duplicated code fragments should return at most one variable of the same type.
  \item Matched branching (\texttt{break}, \texttt{continue}) statements should be accompanied with corresponding matched loop statements.
  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
  \item The mapped statements within the clone fragments should not contain any conditional return statements.
\end{enumerate}

@@

\subsection{Clone refactoring}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process. The main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

>>>>

\subsubsection{Preconditions}
Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \cite{tsantalis2015assessing}:
\begin{enumerate}
  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependences.
  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependences.
  \item The duplicated code fragments should return at most one variable of the same type.
  \item Matched branching (\texttt{break}, \texttt{continue}) statements should be accompanied with corresponding matched loop statements.
  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
  \item The mapped statements within the clone fragments should not contain any conditional return statements.
\end{enumerate}

@@

\subsection{Clone refactoring}
In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. The main focus of this study is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
